# Title
our names here, with the contributions/sections that each of us lead.


### Introduction

Introduction...


### Materials and Methods

And here we write materials and methods...


### Results

Package import:
```{r}
#Library import + csv file import
library(readr)
library(tidyverse)
data <- read.csv("data.csv")
```

Memory game (s) performance by Treatment Group:
```{r}
data %>% #Box plot for memory game vs treatment group
  ggplot(aes(y=memory.game.seconds,x=treatment.group)) +
  geom_boxplot(outliers=FALSE,staplewidth = 0.6) +
  geom_point(color="red",alpha=0.25) + #Translucent points showing each datum
  labs(title="Memory Game Performance (seconds) by Treatment Group",
       y="Memory Game Performance (seconds)",
       x="Treatment Group")
```

Card recall test (/10) performance by treatment group:
```{r}
data %>% #bar chart for card recall test performance (/10) by treatment group
  ggplot(aes(x=cards.10)) +
  geom_bar(color="aquamarine2",fill="aquamarine") +
  labs(title="Card Matching Performance (Out of 10) by Treatment Group",
       x="Card Matching Performance (/10)",
       y="Frequency") +
  scale_x_continuous(n.breaks=10) + #Sets the amount of breaks to 10 (discrete)
  coord_cartesian(xlim=c(0.5,10))+ #Sets the bounds of the graph (0,10)
  facet_wrap(~treatment.group) #Wraps by treatment group
```

Vocabulary recall test (/20) performance by treatment group:
```{r}
data %>% #bar chart for vocabulary recall test by treatment group
  ggplot(aes(x=vocabulary.20)) +
  geom_bar(color="pink2",fill="pink") +
  labs(title="Vocabulary Test Performance (Out of 20) by Treatment Group",
       x="Vocabulary Test Performance (/20)",
       y="Frequency") +
  scale_x_continuous(n.breaks=20)+ #Sets # of breaks to 20 (discrete)
  coord_cartesian(xlim=c(0.5,19.5))+ #Sets bounds of graph (0,20)
  facet_wrap(~treatment.group,dir="v") #Wraps by treatment group
```

Q-Q Plots to test for normality of memory game data for each treatment group:
```{r}
#Memory game Q-Q plot for control group
qqnorm(data$memory.game.seconds[data$treatment.group=="Control"])
qqline(data$memory.game.seconds[data$treatment.group=="Control"])

#Memory game Q-Q plot for anaerobic group
qqnorm(data$memory.game.seconds[data$treatment.group=="Anaerobic"])
qqline(data$memory.game.seconds[data$treatment.group=="Anaerobic"])

#Memory game Q-Q plot for aerobic group
qqnorm(data$memory.game.seconds[data$treatment.group=="Aerobic"])
qqline(data$memory.game.seconds[data$treatment.group=="Aerobic"])

#Data appears roughly normal in all Q-Q plots, deviation from the line likely 
#stems from a small sample size
```

SDs of memory game (s) for each treatment group (ANOVA condition):
```{r}
#Creates a summary table of the memory game performance SD for each group
data %>% summarize( 
"Control SD"=sd(memory.game.seconds[treatment.group=="Control"]),
"Anaerobic SD"=sd(memory.game.seconds[treatment.group=="Anaerobic"]),
"Aerobic SD" = sd(memory.game.seconds[treatment.group=="Aerobic"]))

# None are >2x as large as the others, therefore SD is similar enough for ANOVA
```

One-way ANOVA w/ Tukey HSD Test for memory game performance (s):
```{r}
#Does ANOVA test & saves it to variable
mem_aov <- aov(data$memory.game.seconds~data$treatment.group)
#Prints a summary of the ANOVA test
summary(mem_aov)
#Performs a Tukey HSD test on the ANOVA results to get adjusted p & 95% CI
TukeyHSD(mem_aov,conf.level=0.95)
```

Scatter plot of 7-day exercise history (minutes) vs. each test method (memory game/card recall/vocabulary recall), wrapped by treatment group. Colour of points corresponds to sleep quantity (Less than or greater than 8 hours):
```{r}
#Memory game
data %>%
  #Adds a "total exercise" column combining low/med/high intensity exercise
  mutate(total.exercise = low.intensity.exercise.7d+
           moderate.intensity.exercise.7d+high.intensity.exercise.7d) %>%
  #Adds column for if participants got more/less than 8 hrs of sleep last night
  mutate(sleep.hrs.gl =
           ifelse(sleep.hrs>8,"More than 8 hours", "Less than 8 hours")) %>%
  #Scatter plot w/ 7-day exercise history and memory game performance
  #Coloured by amount of sleep (>/< 8 hrs)
  ggplot(aes(x=total.exercise,y=memory.game.seconds,colour=sleep.hrs.gl)) +
  geom_point() +
  labs(y="Memory Game Performance (seconds)",
       x="Total Exercise in the last 7 days (minutes)",
       title="7-Day Exercise History vs Memory Game Performance",
       color="Sleep (hrs)") +
  facet_wrap(~treatment.group) #Wrap by treatment group

data %>%
  #Adds a "total exercise" column combining low/med/high intensity exercise
  mutate(total.exercise = low.intensity.exercise.7d+
           moderate.intensity.exercise.7d+high.intensity.exercise.7d) %>%
  #Adds column for if participants got more/less than 8 hrs of sleep last night
  mutate(sleep.hrs.gl =
           ifelse(sleep.hrs>8,"More than 8 hours", "Less than 8 hours")) %>%
  #Scatter plot w/ 7-day exercise history and card recall test performance
  #Coloured by amount of sleep (>/< 8 hrs)
  ggplot(aes(x=total.exercise,y=cards.10,colour=sleep.hrs.gl)) +
  geom_point() +
  labs(y="Card Test Performance (/10)",
       x="Total Exercise in the last 7 days (minutes)",
       title="7-Day Exercise History vs Card Recall Performance",
       color="Sleep (hrs)") +
  facet_wrap(~treatment.group) #Wrap by treatment group

data %>%
  #Adds a "total exercise" column combining low/med/high intensity exercise
  mutate(total.exercise = low.intensity.exercise.7d+
           moderate.intensity.exercise.7d+high.intensity.exercise.7d) %>%
  #Adds column for if participants got more/less than 8 hrs of sleep last night
  mutate(sleep.hrs.gl =
           ifelse(sleep.hrs>8,"More than 8 hours", "Less than 8 hours")) %>%
  #Scatter plot w/ 7-day exercise history and vocabulary recall test performance
  #Coloured by amount of sleep (>/< 8 hrs)
  ggplot(aes(x=total.exercise,y=vocabulary.20,colour=sleep.hrs.gl)) +
  geom_point() +
  labs(y="Vocabulary Test Performance (/20)",
       x="Total Exercise in the last 7 days (minutes)",
       title="7-Day Exercise History vs Vocabulary Recall Performance",
       color="Sleep (hrs)") +
  facet_wrap(~treatment.group) #Wrapped by treatment group
```


Bootstrap + CI of memory game for each treatment group:
```{r}
set.seed(288)

#Control group
n<-31 #Amount of sampled individuals
reps<-1000 #Set repetition amount
boot_means<-vector("numeric",reps) #Initialize vector

for(i in 1:reps){ #Bootstrapping
boot_stat<-data %>%
  filter(treatment.group=="Control") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(memory.game.seconds))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for getting limits
limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper/lower 2.5% for 95% CI
print("Control group, 95% CI") #Make it easier to read
print(limits) #95% Confidence Interval


#Aerobic group
n<-33 #amount of people
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Aerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(memory.game.seconds[treatment.group=="Aerobic"]))
boot_means[i]<-boot_stat$mean_perf
}
boot_means<-data_frame(m_perf=boot_means) #To dataframe for getting limits
limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper/lower 2.5% for 95% CI
print("Aerobic group, 95% CI") #Makes it slightly more readable
print(limits) #95% Confidence Interval


#Anaerobic group
n<-33 #amount of people
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Anaerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(memory.game.seconds[treatment.group=="Anaerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for getting limits
limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper/lower 2.5% for 95% CI
print("Anaerobic group, 95% CI") #Make it easier to read
print(limits) #95% Confidence Interval
```

Bootstrap + CI of Card Game for each treatment group:
```{r}
set.seed(288)

#Control group
n<-31 #Amount of people
reps<-1000 #Number of repetitions
boot_means<-vector("numeric",reps) #Initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Control") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(cards.10[treatment.group=="Control"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for limits
limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #upper/lower 2.5% for 95% CI
print("Control group, 95% CI") #Visual clarity
print(limits) #95% Confidence Interval


#Aerobic group
n<-33 #Number of people
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Aerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(cards.10[treatment.group=="Aerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for limits
limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #upper/lower 2.5% for 95% CI
print("Aerobic group, 95% CI") #Visual clarity
print(limits) #95% Confidence Interval


#Anaerobic group
n<-33 #Amount of people
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Anaerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(cards.10[treatment.group=="Anaerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for limits
limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper/lower 2.5% for 95% CI
print("Anaerobic group, 95% CI") #visual clarity
print(limits) #95% Confidence Interval
```

Bootstrap + CI of Vocabulary game for each treatment group:
```{r}
set.seed(288)

#Control group
n<-31 #Amount of people
reps<-1000 #Amount of reps
boot_means<-vector("numeric",reps) #Initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Control") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(vocabulary.20[treatment.group=="Control"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for limits
limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper/lower 2.5% for 95% CI
print("Control group, 95% CI") #Visual clarity
print(limits) #95% Confidence Interval


#Aerobic group
n<-33 #Amount of people
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Aerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(vocabulary.20[treatment.group=="Aerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for limits
limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #upper/lower 2.5% for 95% CI
print("Aerobic group, 95% CI") #Visual clarity
print(limits) #95% Confidence Interval


#Anaerobic group
n<-33 #Amount of people
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Anaerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(vocabulary.20[treatment.group=="Anaerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for limits
limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper/lower 2.5% for 95% CI
print("Anaerobic group, 95% CI") #visual clarity
print(limits) #95% Confidence Interval
```

Simulation-based hypothesis test ($H_0: \mu_{ctrl}-\mu_{aerobic} = 0$, $H_1: \mu_{ctrl}-\mu_{aerobic} \neq 0$) for each test type (memory/card/vocabulary):
```{r}
set.seed(288)

#Memory test
reps<-1000 #number of reps
sim_stats<-vector("numeric", length=reps) #Initialize vector
#Calculate test statistic
test_stat <- (mean(data$memory.game.seconds[data$treatment.group=="Control"])
-mean(data$memory.game.seconds[data$treatment.group=="Aerobic"]))

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(memory.game.seconds))
  sim_stats[i]<-(sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]
  -sim_x_bar$m_perf[sim_x_bar$treatment.group=="Aerobic"]) #Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #To dataframe
diff_m_perf %>% summarize(n=n(), #sample size/test statistic/p value
                          "Test statistic" = test_stat,
                          p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat)))

#Card recall test
sim_stats<-vector("numeric", length=reps) #Re-initialize vector
#Calculate test statistic
test_stat <- (mean(data$cards.10[data$treatment.group=="Control"])
-mean(data$cards.10[data$treatment.group=="Aerobic"]))

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(cards.10))
  sim_stats[i]<-(sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]
  -sim_x_bar$m_perf[sim_x_bar$treatment.group=="Aerobic"]) #Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #To dataframe
diff_m_perf %>% summarize(n=n(), #sample size/test statistic/p value
                          "Test statistic" = test_stat,
                          p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat)))

#Vocabulary recall test
sim_stats<-vector("numeric", length=reps) #Re-initialize vector
#Calculate test statistic
test_stat <- (mean(data$vocabulary.20[data$treatment.group=="Control"])
-mean(data$vocabulary.20[data$treatment.group=="Aerobic"]))

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(vocabulary.20))
  sim_stats[i]<-(sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]
  -sim_x_bar$m_perf[sim_x_bar$treatment.group=="Aerobic"]) #Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #To dataframe
diff_m_perf %>% summarize(n=n(), #sample size/test statistic/p value
                          "Test statistic" = test_stat,
                          p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat)))

```

Simulation-based hypothesis test ($H_0: \mu_{ctrl}-\mu_{anaerobic} = 0$, $H_1: \mu_{ctrl}-\mu_{anaerobic} \neq 0$) for each test type (memory/card/vocabulary):
```{r}
set.seed(288)

#Memory test
reps<-1000 #Set # of reps
sim_stats<-vector("numeric", length=reps) #Initialize vector
#Calculate test statistic
test_stat = mean((data$memory.game.seconds[data$treatment.group=="Control"])
-mean(data$memory.game.seconds[data$treatment.group=="Anaerobic"]))

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(memory.game.seconds))
  sim_stats[i]<-(sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]
  -sim_x_bar$m_perf[sim_x_bar$treatment.group=="Anaerobic"])#Simulated statistic
}
diff_m_perf<-data_frame(diff=sim_stats) #To dataframe
diff_m_perf %>% summarize(n=n(), #sample size/test statistic/p value
                          "Test statistic" = test_stat,
                          p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat)))

#Card recall test
sim_stats<-vector("numeric", length=reps) #Re-initialize vector
#Calculate test statistic
test_stat = (mean(data$cards.10[data$treatment.group=="Control"])
-mean(data$cards.10[data$treatment.group=="Anaerobic"])) 

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(cards.10))
  sim_stats[i]<-(sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]
  -sim_x_bar$m_perf[sim_x_bar$treatment.group=="Anaerobic"])#Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #To dataframe
diff_m_perf %>% summarize(n=n(), #sample size/test statistic/p value
                          "Test statistic" = test_stat,
                          p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat)))

#Vocabulary recall test
sim_stats<-vector("numeric", length=reps)
#Calculate test statistic
test_stat = (mean(data$vocabulary.20[data$treatment.group=="Control"])
-mean(data$vocabulary.20[data$treatment.group=="Anaerobic"]))

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(vocabulary.20))

  sim_stats[i]<-(sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]
  -sim_x_bar$m_perf[sim_x_bar$treatment.group=="Anaerobic"])#Simulated statistic
}
diff_m_perf<-data_frame(diff=sim_stats) #To dataframe
diff_m_perf %>% summarize(n=n(), #sample size/test statistic/p value
                          "Test statistic" = test_stat,
                          p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat)))

```

Simulation-based hypothesis test ($H_0: \mu_{aerobic}-\mu_{anaerobic} = 0$, $H_1: \mu_{aerobic}-\mu_{anaerobic} \neq 0$) for each test type (memory/card/vocabulary):
```{r}
set.seed(288)

#Memory test
reps<-1000 #Set # of reps
sim_stats<-vector("numeric", length=reps) #Initialize vector
#Calculate test statistic
test_stat = mean((data$memory.game.seconds[data$treatment.group=="Aerobic"])
-mean(data$memory.game.seconds[data$treatment.group=="Anaerobic"]))

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(memory.game.seconds))
  sim_stats[i]<-(sim_x_bar$m_perf[sim_x_bar$treatment.group=="Aerobic"]
  -sim_x_bar$m_perf[sim_x_bar$treatment.group=="Anaerobic"])#Simulated statistic
}
diff_m_perf<-data_frame(diff=sim_stats) #To dataframe
diff_m_perf %>% summarize(n=n(), #sample size/test statistic/p value
                          "Test statistic" = test_stat,
                          p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat)))

#Card recall test
sim_stats<-vector("numeric", length=reps) #Re-initialize vector
#Calculate test statistic
test_stat = mean((data$cards.10[data$treatment.group=="Aerobic"])
-mean(data$cards.10[data$treatment.group=="Anaerobic"]))

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(cards.10))
  sim_stats[i]<-(sim_x_bar$m_perf[sim_x_bar$treatment.group=="Aerobic"]
  -sim_x_bar$m_perf[sim_x_bar$treatment.group=="Anaerobic"])#Simulated statistic
}
diff_m_perf<-data_frame(diff=sim_stats) #To dataframe
diff_m_perf %>% summarize(n=n(), #sample size/test statistic/p value
                          "Test statistic" = test_stat,
                          p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat)))

#Vocabulary Recall test
sim_stats<-vector("numeric", length=reps) #Re-initialize vector
#Calculate test statistic
test_stat = mean((data$vocabulary.20[data$treatment.group=="Aerobic"])
-mean(data$vocabulary.20[data$treatment.group=="Anaerobic"]))

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(vocabulary.20))
  sim_stats[i]<-(sim_x_bar$m_perf[sim_x_bar$treatment.group=="Aerobic"]
  -sim_x_bar$m_perf[sim_x_bar$treatment.group=="Anaerobic"])#Simulated statistic
}
diff_m_perf<-data_frame(diff=sim_stats) #To dataframe
diff_m_perf %>% summarize(n=n(), #sample size/test statistic/p value
                          "Test statistic" = test_stat,
                          p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat)))
```
### Conclusions 

etc


### Discussion

etc


### References

etc


### Appendixes

etc