# Title here.
our names here, with the contributions/sections that each of us lead.


### Introduction

Introduction...


### Materials and Methods

And here we write materials and methods...


### Results


```{r}
#File import
library(readr)
library(tidyverse)
data <- read.csv("data.csv")
```


Comparisons:
```{r}
data %>% #box plot for memory game vs. tg 
  ggplot(aes(y=memory.game.seconds,x=treatment.group)) +
  geom_boxplot(outliers=FALSE,staplewidth = 0.6) +
  geom_point(color="red",alpha=0.25) +
  labs(title="Memory Game Performance (seconds) by Treatment Group",
       y="Memory Game Performance (seconds)",
       x="Treatment Group")
```

```{r}
data %>% #box plot for card game vs. tg
  ggplot(aes(x=cards.10)) +
  geom_bar(color="aquamarine2",fill="aquamarine") +
  labs(title="Card Matching Performance (Out of 10) by Treatment Group",
       x="Card Matching Performance (/10)",
       y="Frequency") +
  scale_x_continuous(n.breaks=10) +
  coord_cartesian(xlim=c(0.5,10))+
  facet_wrap(~treatment.group)
```

```{r}
data %>% #box plot for vocab test vs. tg
  ggplot(aes(x=vocabulary.20)) +
  geom_bar(color="pink2",fill="pink") +
  labs(title="Vocabulary Test Performance (Out of 20) by Treatment Group",
       x="Vocabulary Test Performance (/20)",
       y="Frequency") +
  scale_x_continuous(n.breaks=20)+
  coord_cartesian(xlim=c(0.5,19.5))+
  facet_wrap(~treatment.group,dir="v")
```

```{r}
qqnorm(data$memory.game.seconds[data$treatment.group=="Control"])
qqline(data$memory.game.seconds[data$treatment.group=="Control"])

qqnorm(data$memory.game.seconds[data$treatment.group=="Anaerobic"])
qqline(data$memory.game.seconds[data$treatment.group=="Anaerobic"])

qqnorm(data$memory.game.seconds[data$treatment.group=="Aerobic"])
qqline(data$memory.game.seconds[data$treatment.group=="Aerobic"])
```

```{r}
sd(data$memory.game.seconds[data$treatment.group=="Control"])
sd(data$memory.game.seconds[data$treatment.group=="Anaerobic"])
sd(data$memory.game.seconds[data$treatment.group=="Aerobic"])
# None are >2x as large as the others, therefore SD is similar enough
#H0: mu(control) = mu(anaerobic) = mu(aerobic)
#H1: at least one differs
mem_aov <- aov(data$memory.game.seconds~data$treatment.group)
summary(mem_aov)
TukeyHSD(mem_aov,conf.level=0.95)
```

```{r}
data %>%
  mutate(total.exercise = low.intensity.exercise.7d+moderate.intensity.exercise.7d+high.intensity.exercise.7d) %>%
  mutate(sleep.hrs.gl = ifelse(sleep.hrs>8,"More than 8 hours", "Less than 8 hours")) %>%
  ggplot(aes(x=total.exercise,y=memory.game.seconds,colour=sleep.hrs.gl)) +
  geom_point() +
  labs(y="Memory Game Performance (seconds)", x="Total Exercise in the last 7 days (minutes)", title="7-Day Exercise History vs Memory Game Performance",color="Sleep (hrs)") +
  facet_wrap(~treatment.group)

data %>%
  mutate(total.exercise = low.intensity.exercise.7d+moderate.intensity.exercise.7d+high.intensity.exercise.7d) %>%
  mutate(sleep.hrs.gl = ifelse(sleep.hrs>8,"More than 8 hours", "Less than 8 hours")) %>%
  ggplot(aes(x=total.exercise,y=cards.10,colour=sleep.hrs.gl)) +
  geom_point() +
  labs(y="Card Test Performance (/10)", x="Total Exercise in the last 7 days (minutes)", title="7-Day Exercise History vs Card Recall Performance",color="Sleep (hrs)") +
  facet_wrap(~treatment.group)

data %>%
  mutate(total.exercise = low.intensity.exercise.7d+moderate.intensity.exercise.7d+high.intensity.exercise.7d) %>%
  mutate(sleep.hrs.gl = ifelse(sleep.hrs>8,"More than 8 hours", "Less than 8 hours")) %>%
  ggplot(aes(x=total.exercise,y=vocabulary.20,colour=sleep.hrs.gl)) +
  geom_point() +
  labs(y="Vocabulary Test Performance (/20)", x="Total Exercise in the last 7 days (minutes)", title="7-Day Exercise History vs Vocabulary Recall Performance",color="Sleep (hrs)") +
  facet_wrap(~treatment.group)
```

```{r}

```

```{r}

data %>% summarize("Mean" = mean(memory.game.seconds),
                   "Median/50th Quantile" = median(memory.game.seconds),
                   "Standard Deviation" = sd(memory.game.seconds),
                   "Minimum Value" = min(memory.game.seconds),
                   "Maximum Value" = max(memory.game.seconds),
                   "25th Quantile" = quantile(memory.game.seconds,0.25),
                   "75th Quantile" = quantile(memory.game.seconds,0.75))
data %>% summarize("Mean" = mean(cards.10),
                   "Median/50th Quantile" = median(cards.10),
                   "Standard Deviation" = sd(cards.10),
                   "Minimum Value" = min(cards.10),
                   "Maximum Value" = max(cards.10),
                   "25th Quantile" = quantile(cards.10,0.25),
                   "75th Quantile" = quantile(cards.10,0.75))
data %>% summarize("Mean" = mean(vocabulary.20),
                   "Median/50th Quantile" = median(vocabulary.20),
                   "Standard Deviation" = sd(vocabulary.20),
                   "Minimum Value" = min(vocabulary.20),
                   "Maximum Value" = max(vocabulary.20),
                   "25th Quantile" = quantile(vocabulary.20,0.25),
                   "75th Quantile" = quantile(vocabulary.20,0.75))
```


Bootstrap of Memory Game
```{r}
set.seed(288)

n<-31 #Amount of sampled individuals per rep
reps<-1000 #Set repetition amount
boot_means<-vector("numeric",reps) #Initialize vector

for(i in 1:reps){ #Bootstrapping
boot_stat<-data %>%
  filter(treatment.group=="Control") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(memory.game.seconds))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #Convert to dataframe for ggplot

limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper & lower 2.5% for 95% CI

boot_means %>% ggplot(aes(x=m_perf)) +  #Generate a histogram w/ CI
  geom_histogram(binwidth=0.5, colour="black",fill="grey") + 
  labs(x="Bootstrap means of memory game performance (seconds), control group (n=31)",
       y="Frequency") +
  scale_x_continuous(n.breaks = 10) +
  geom_vline(xintercept=limits[1], colour="blue",linetype="dotdash", size=0.8) +  
  geom_vline(xintercept=limits[2], colour="blue",linetype="dotdash", size=0.8)
print("Control group, 95% CI") #Make it easier to read
print(limits) #95% Confidence Interval


n<-33 #amount of ppl
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Aerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(memory.game.seconds[treatment.group=="Aerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #Convert to dataframe for ggplot

limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper and lower 2.5% for 95% CI

boot_means %>% ggplot(aes(x=m_perf)) + #Histogram w/ 95% CI
  geom_histogram(binwidth=0.5, colour="black",fill="grey") + 
  labs(x="Bootstrap means of memory game performance (seconds), aerobic group (n=33)",
       y="Frequency") +
  scale_x_continuous(n.breaks = 10) +
  geom_vline(xintercept=limits[1], colour="blue",linetype="dotdash", size=0.8) +  
  geom_vline(xintercept=limits[2], colour="blue",linetype="dotdash", size=0.8)
print("Aerobic group, 95% CI") #Makes it slightly more readable
print(limits) #95% Confidence Interval


n<-33 #number of ppl
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Anaerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(memory.game.seconds[treatment.group=="Anaerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for ggplot

limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #upper and lower 2.5% for 95% CI

boot_means %>% ggplot(aes(x=m_perf)) + #Histogram w/ CI
  geom_histogram(binwidth=0.5, colour="black",fill="grey") + 
  labs(x="Bootstrap means of memory game performance (seconds), anaerobic group (n=33)",
       y="Frequency") +
  scale_x_continuous(n.breaks = 10) +
  geom_vline(xintercept=limits[1], colour="blue",linetype="dotdash", size=0.8) +  
  geom_vline(xintercept=limits[2], colour="blue",linetype="dotdash", size=0.8)
print("Anaerobic group, 95% CI") #Make it easier to read
print(limits) #95% Confidence Interval
```

Bootstrap of Card Game
```{r}
set.seed(288)
n<-31 #Number of ppl
reps<-1000 #Number of repetitions
boot_means<-vector("numeric",reps) #Initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Control") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(cards.10[treatment.group=="Control"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for ggplot

limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #upper/lower 2.5% for 95% CI

boot_means %>% ggplot(aes(x=m_perf)) + #Histogram w/ CI
  geom_histogram(binwidth=1, colour="black",fill="grey") + 
  labs(x="Bootstrap means of card game performance (/10), control group (n=31)",
       y="Frequency") +
  geom_vline(xintercept=limits[1], colour="blue",linetype="dotdash", size=0.8) +  
  geom_vline(xintercept=limits[2], colour="blue",linetype="dotdash", size=0.8)
print("Control group, 95% CI") #Visual clarity
print(limits) #95% Confidence Interval


n<-33 #Number of ppl
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Aerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(cards.10[treatment.group=="Aerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for ggplot

limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #upper/lower 2.5% for 95% CI

boot_means %>% ggplot(aes(x=m_perf)) + #Histogram w/ CI
  geom_histogram(binwidth=1, colour="black",fill="grey") + 
  labs(x="Bootstrap means of card game performance (/10), aerobic group (n=33)",
       y="Frequency") +
  geom_vline(xintercept=limits[1], colour="blue",linetype="dotdash", size=0.8) +  
  geom_vline(xintercept=limits[2], colour="blue",linetype="dotdash", size=0.8)
print("Aerobic group, 95% CI") #Visual clarity
print(limits) #95% Confidence Interval


n<-33 #Amount of ppl
boot_means<-vector("numeric",reps) #Initialize

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Anaerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(vocabulary.20[treatment.group=="Anaerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for ggplot

limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper/lower 2.5% for 95% CI

boot_means %>% ggplot(aes(x=m_perf)) + #Histogram w/ CI
  geom_histogram(binwidth=1, colour="black",fill="grey") + 
  labs(x="Bootstrap means of card game performance (/10), anaerobic group (n=33)",
       y="Frequency") +
  geom_vline(xintercept=limits[1], colour="blue",linetype="dotdash", size=0.8) +  
  geom_vline(xintercept=limits[2], colour="blue",linetype="dotdash", size=0.8)
print("Anaerobic group, 95% CI") #visual clarity
print(limits) #95% Confidence Interval
```

Bootstrap of Vocabulary Game
```{r}
set.seed(288)
n<-31 #amt of ppl
reps<-1000 #amt of reps
boot_means<-vector("numeric",reps) #Initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Control") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(vocabulary.20[treatment.group=="Control"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for ggplot

limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper/lower 2.5% for 95% CI

boot_means %>% ggplot(aes(x=m_perf)) + #Histogram w/ CI
  geom_histogram(binwidth=1, colour="black",fill="grey") + 
  labs(x="Bootstrap means of vocabulary game performance (/10), control group (n=31)",
       y="Frequency") +
  geom_vline(xintercept=limits[1], colour="blue",linetype="dotdash", size=0.8) +  
  geom_vline(xintercept=limits[2], colour="blue",linetype="dotdash", size=0.8)
print("Control group, 95% CI") #Visual clarity
print(limits) #95% Confidence Interval


n<-33 #amt of ppl
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Aerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(vocabulary.20[treatment.group=="Aerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for ggplot

limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #upper/lower 2.5% for 95% CI

boot_means %>% ggplot(aes(x=m_perf)) + #Histogram w/ CI
  geom_histogram(binwidth=1, colour="black",fill="grey") + 
  labs(x="Bootstrap means of vocabulary game performance (/10), aerobic group (n=33)",
       y="Frequency") +
  geom_vline(xintercept=limits[1], colour="blue",linetype="dotdash", size=0.8) +  
  geom_vline(xintercept=limits[2], colour="blue",linetype="dotdash", size=0.8)
print("Aerobic group, 95% CI") #Visual clarity
print(limits) #95% Confidence Interval


n<-33 #Amt of ppl
boot_means<-vector("numeric",reps) #Re-initialize vector

for(i in 1:reps){ #Bootstrap
boot_stat<-data %>%
  filter(treatment.group=="Anaerobic") %>%
  sample_n(size=n,replace=TRUE) %>%
  summarise(mean_perf=mean(vocabulary.20[treatment.group=="Anaerobic"]))
boot_means[i]<-boot_stat$mean_perf
}

boot_means<-data_frame(m_perf=boot_means) #To dataframe for ggplot

limits<-quantile(boot_means$m_perf,c(0.025,0.975)) #Upper/lower 2.5% for 95% CI

boot_means %>% ggplot(aes(x=m_perf)) + #Histogram w/ CI
  geom_histogram(binwidth=1, colour="black",fill="grey") + 
  labs(x="Bootstrap means of vocabulary game performance (/10), anaerobic group (n=33)",
       y="Frequency") +
  geom_vline(xintercept=limits[1], colour="blue",linetype="dotdash", size=0.8) +  
  geom_vline(xintercept=limits[2], colour="blue",linetype="dotdash", size=0.8)
print("Anaerobic group, 95% CI") #visual clarity
print(limits) #95% Confidence Interval
```

Hypothesis test ($\mu_{ctrl}-\mu_{aerobic}$) for each test
```{r}
set.seed(288)

#Memory test
reps<-1000 #number of reps
sim_stats<-vector("numeric", length=reps) #Initialize vector
test_stat = mean(data$memory.game.seconds[data$treatment.group=="Control"])-mean(data$memory.game.seconds[data$treatment.group=="Aerobic"]) #Get test stat 

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(memory.game.seconds))

  sim_stats[i]<-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Aerobic"] #Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #convert to dataframe for ggplot

diff_m_perf %>% ggplot(aes(x=diff)) + #Histogram for two-tailed hypothesis test
  geom_histogram(binwidth=0.5,colour="black", fill="grey") +
  labs(x="Difference in sample mean of memory test by exercise type (Control-Aerobic)",
       y="Frequency") +
  geom_vline(xintercept=abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8) +
  geom_vline(xintercept=-abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8)
diff_m_perf %>% summarize(n=n(), p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat))) #Calculate p-value




#Card recall test
sim_stats<-vector("numeric", length=reps) #Re-initialize vector
test_stat = mean(data$cards.10[data$treatment.group=="Control"])-mean(data$cards.10[data$treatment.group=="Aerobic"]) #Calculate test statistic

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(cards.10))

  sim_stats[i]<-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Aerobic"] #Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #To dataframe for ggplot

diff_m_perf %>% ggplot(aes(x=diff)) + #Histogram for 2-tailed hypothesis test
  geom_histogram(binwidth=1,colour="black", fill="grey") +
  labs(x="Difference in sample mean of card recall test by exercise type (Control-Aerobic)",
       y="Frequency") +
  geom_vline(xintercept=abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8) +
  geom_vline(xintercept=-abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8)
diff_m_perf %>% summarize(n=n(), p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat))) #Calculate p value


#Vocabulary recall test
sim_stats<-vector("numeric", length=reps) #Re-initialize vector
test_stat = mean(data$vocabulary.20[data$treatment.group=="Control"])-mean(data$vocabulary.20[data$treatment.group=="Aerobic"]) #Calculate test statistic

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(vocabulary.20))

  sim_stats[i]<-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Aerobic"] #Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #To dataframe for ggplot

diff_m_perf %>% ggplot(aes(x=diff)) + #Histogram for 2-tailed hypothesis test
  geom_histogram(binwidth=1,colour="black", fill="grey") +
  labs(x="Difference in sample mean of vocabulary recall test by exercise type (Control-Aerobic)",
       y="Frequency") +
  geom_vline(xintercept=abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8) +
  geom_vline(xintercept=-abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8)
diff_m_perf %>% summarize(n=n(), p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat))) #Calculate p value

```
Hypothesis test ($\mu_{ctrl}-\mu_{anaerobic}$) for each test
```{r}
set.seed(288)

#Memory test
reps<-1000 #Set # of reps
sim_stats<-vector("numeric", length=reps) #Initialize vector
test_stat = mean(data$memory.game.seconds[data$treatment.group=="Control"])-mean(data$memory.game.seconds[data$treatment.group=="Anaerobic"]) #Calculate test statistic

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(memory.game.seconds))
  sim_stats[i]<-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Anaerobic"] #Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #To dataframe for ggplot

diff_m_perf %>% ggplot(aes(x=diff)) + #Histogram for 2-tailed hypothesis test
  geom_histogram(binwidth=0.5,colour="black", fill="grey") +
  labs(x="Difference in sample mean of memory test by exercise type (Control-Anaerobic)",
       y="Frequency") +
  geom_vline(xintercept=abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8) +
  geom_vline(xintercept=-abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8)
diff_m_perf %>% summarize(n=n(), p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat))) #Calculate p-value





#Card recall test
sim_stats<-vector("numeric", length=reps) #Re-initialize vector
test_stat = mean(data$cards.10[data$treatment.group=="Control"])-mean(data$cards.10[data$treatment.group=="Anaerobic"]) #Calculate test statistic

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(cards.10))

  sim_stats[i]<-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Anaerobic"] #Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #to dataframe for ggplot

diff_m_perf %>% ggplot(aes(x=diff)) + #Histogram for 2-tailed hypothesis test
  geom_histogram(binwidth=0.5,colour="black", fill="grey") +
  labs(x="Difference in sample mean of card recall test by exercise type (Control-Anaerobic)",
       y="Frequency") +
  geom_vline(xintercept=abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8) +
  geom_vline(xintercept=-abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8)
diff_m_perf %>% summarize(n=n(), p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat))) #Calculate p-value




#Vocabulary recall test
sim_stats<-vector("numeric", length=reps)
test_stat = mean(data$vocabulary.20[data$treatment.group=="Control"])-mean(data$vocabulary.20[data$treatment.group=="Anaerobic"]) #Calculate test statistic

for (i in 1:reps) { #Simulated re-sampling
  sim<-data %>%
  mutate(treatment.group=sample(treatment.group))
  
  sim_x_bar<-sim %>%
  group_by(treatment.group) %>%
  summarise(m_perf=mean(vocabulary.20))

  sim_stats[i]<-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Control"]-sim_x_bar$m_perf[sim_x_bar$treatment.group=="Anaerobic"] #Simulated statistic
}

diff_m_perf<-data_frame(diff=sim_stats) #to dataframe for ggplot

diff_m_perf %>% ggplot(aes(x=diff)) + #Histogram for 2-tailed hypothesis test
  geom_histogram(binwidth=0.5,colour="black", fill="grey") +
  labs(x="Difference in sample mean of vocabulary recall test by exercise type (Control-Anaerobic)",
       y="Frequency") +
  geom_vline(xintercept=abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8) +
  geom_vline(xintercept=-abs(test_stat), colour="darkgreen",linetype = "dotdash",size=0.8)
diff_m_perf %>% summarize(n=n(), p=mean(diff<=-abs(test_stat)|diff>=abs(test_stat))) #Calculate p-value

```

### Conclusions 

etc


### Discussion

etc


### References

etc


### Appendixes

etc